### 2017-01-30 doc/manuscript.Rmd
Changed title to be results agnostic

Title: Fatty acids involved in de novo lipogenesis within the serum
triacylglycerol fraction strongly predict lower insulin sensitivity.

>>>>

Title: Composition of fatty acids within the serum triacylglycerol fraction and 
the association with the pathogenesis of diabetes in a population at-risk for 
diabetes
